---
title: "Weiss Review Reports"
output:
  pdf_document: default
  html_document: default
font-family: Arial
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



```{r cars}
weiss_fall2021 <- read.csv(file="/Users/parthukalva/Downloads/Weiss_merge/Fall 2021 Application Scores_Compiled.xlsx - Sheet1 (1).csv", header=TRUE, sep=",", stringsAsFactors = FALSE)

num <- weiss_fall2021$number[i]
firstname <- weiss_fall2021$First.name[i]
lastname <- weiss_fall2021$Last.Name[i]
currentposition <- weiss_fall2021$Current.Position[i]
department <- weiss_fall2021$Department[i]
school <- weiss_fall2021$School[i]
copi1 <- weiss_fall2021$MTCoInvestigatorFull.Name.1[i]
copi2 <- weiss_fall2021$MTCoInvestigatorFull.Name.2[i]
copi3 <- weiss_fall2021$MTCoInvestigatorFull.Name.3[i]
copi4 <- weiss_fall2021$MTCoInvestigatorFull.Name.4[i]

title <- weiss_fall2021$Project.title[i]
amount <- weiss_fall2021$Amount[i]
chaircomment <- weiss_fall2021$Committee.Chair.Comments[i]
sheperd_high <- weiss_fall2021$Shepherd.High[i]
sheperd_low <- weiss_fall2021$Shepherd.Low[i]

simple_avg <- weiss_fall2021$Average.w.AB[i]
weighted_avg <- weiss_fall2021$Weighted.AVG[i]
kl <- weiss_fall2021$KL[i]
mb <- weiss_fall2021$MB[i]
aw <- weiss_fall2021$AW[i]
tm <- weiss_fall2021$TM[i]
es <- weiss_fall2021$ES[i]
ob <- weiss_fall2021$OB[i]
sc <- weiss_fall2021$SC[i]
ab <- weiss_fall2021$AB[i]
mk <- weiss_fall2021$MK[i]

applicant_commentKL <- weiss_fall2021$KL.Applicant[i]
committee_commentKL <- weiss_fall2021$KL.Committee[i]
cost_commentKL <- weiss_fall2021$KL.Cost[i]

applicant_commentMB <- weiss_fall2021$MB.Applicant[i]
committee_commentMB <- weiss_fall2021$MB.Committee[i]
cost_commentMB <- weiss_fall2021$MB.Cost[i]

applicant_commentAW <- weiss_fall2021$AW.applicant[i]
committee_commentAW <- weiss_fall2021$AW.Committee[i]
cost_commentAW <- weiss_fall2021$AW.Cost[i]

applicant_commentTM <- weiss_fall2021$TM.Applicant[i]
committee_commentTM <- weiss_fall2021$TM.Committee[i]
cost_commentTM <- weiss_fall2021$TM.Cost[i]

applicant_commentES <- weiss_fall2021$ES.Applicant[i]
committee_commentES <- weiss_fall2021$ES.Committee[i]
cost_commentES <- weiss_fall2021$ES.Cost[i]

applicant_commentOB <- weiss_fall2021$OB.Applicant[i]
committee_commentOB <- weiss_fall2021$OB.Committee[i]
cost_commentOB <- weiss_fall2021$OB.Cost[i]

applicant_commentSC <- weiss_fall2021$SC.Applicant[i]
committee_commentSC <- weiss_fall2021$SC.Committee[i]
cost_commentSC <- weiss_fall2021$SC.Cost[i]

applicant_commentAB <- weiss_fall2021$AB.Applicant[i]
committee_commentAB <- weiss_fall2021$AB.Committee[i]
cost_commentAB <- weiss_fall2021$AB.Cost[i]

applicant_commentMK <- weiss_fall2021$MK.Applicant[i]
committee_commentMK <- weiss_fall2021$MK.Committee[i]
cost_commentMK <- weiss_fall2021$MK.Cost[i]

marginalbenefit <- weiss_fall2021$Sr.Faculty..The.descriptions.provided.of.marginal.benefit.will.also.be.closely.reviewed.for.senior.faculty.applications.[i]
path_to_scale <- weiss_fall2021$Sr.Faculty..The.descriptions.provided.of.pathway.to.scale..will.also.be.closely.reviewed.for.senior.faculty.applications[i]
```

## Number

`r num`

## PI

**`r firstname`**, **`r lastname`**, `r currentposition`,`r department`, `r school`

## CO PIs

`r copi1` `r copi2` `r copi3` `r copi4`

## PROJECT TITLE

`r title`

## AMOUNT REQUESTED

`r amount`

## Committee Chair Comments

`r chaircomment`

## Sheperd High

`r sheperd_high`

## Sheperd Low

`r sheperd_low`

## Committee Scores

Reviewer    | Score
----------- | -------------
KL          | `r kl`
MB          | `r mb` 
AW          | `r aw`
TM          | `r tm` 
ES          | `r es`
OB          | `r ob` 
SC          | `r sc`
AB          | `r ab` 
MK          | `r mk` 
Simple AVG  | `r simple_avg`
Weighted AVG | `r weighted_avg`

## Committee Comments

Reviewer           |  Applicant Comments     | Committee Comments      | Cost Comments      |
------------------ | ----------------------- | ----------------------- | ------------------ | 
Kevin `r kl`       | `r applicant_commentKL` | `r committee_commentKL` | `r cost_commentKL` |
Marianne `r mb`    | `r applicant_commentMB` | `r committee_commentMB` | `r cost_commentMB` |
Andrew `r aw`      | `r applicant_commentAW` | `r committee_commentAW` | `r cost_commentAW` |
Ted `r tm`         | `r applicant_commentTM` | `r committee_commentTM` | `r cost_commentTM` |
Ernesto `r es`     | `r applicant_commentES` | `r committee_commentES` | `r cost_commentES` |
Oriana `r ob`      | `r applicant_commentOB` | `r committee_commentOB` | `r cost_commentOB` |
Shawn `r sc`       | `r applicant_commentSC` | `r committee_commentSC` | `r cost_commentSC` |
Abhijit `r ab`     | `r applicant_commentAB` | `r committee_commentAB` | `r cost_commentAB` |
Michael `r mk`     | `r applicant_commentMK` | `r committee_commentMK` | `r cost_commentMK` |


## Senior Faculty Text For Extra Consideration

**Marginal Benefit**

`r marginalbenefit`

**Pathways to Scale**

`r path_to_scale`
